Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-10-31 doc/prelim/presentation/prelim_presentation.tex
finished nonlinear section

@@

@@

@@

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Progress to Date}

%%---------------------------------------------------------------------------%%
\begin{frame}{Progress to Date}

%%---------------------------------------------------------------------------%%
\begin{frame}{Progress to Date}

>>>>

%%---------------------------------------------------------------------------%%
\begin{frame}{Generalization of MCSA for Linear Problems}

@@

  \begin{itemize}
  \item Richardson iteration and residual computation require parallel
    matrix-vector multiply and parallel vector update
  \item This work will generate a parallel adjoint Neumann-Ulam solver 
  \item Application of correction requires parallel vector update
  \item Convergence checks through parallel norm computation
  \end{itemize}

@@

  \begin{algorithm}[H]
    \begin{algorithmic}[1]
      \STATE $k := 0$
      \WHILE{$||\ve{F}(\ve{u}^{k})|| > \epsilon ||\ve{F}(\ve{u}^{0})||$}
      \STATE $\ve{J}(\ve{u}^{k}) \leftarrow AD(\ve{F}(\ve{u}^k))$
      \COMMENT{Automatic differentation}
      \STATE $\ve{J}(\ve{u}^k) \delta \ve{u}^k = -\ve{F}(\ve{u}^{k})$
      \COMMENT{Solve for the Newton correction with MCSA}
      \STATE $\ve{u}^{k+1} \leftarrow \ve{u}^k + \delta \ve{u}^k$
      \STATE $k \leftarrow k+1$
      \ENDWHILE
    \end{algorithmic}
    \caption{FANM}
  \end{algorithm}

  \begin{itemize}
  \item Modern FAD packages are parallelized using element-level assembly
  \item This work will generate a parallel MCSA solver
  \item Application of the Newton correction requires a parallel vector
    update
  \item Convergence checks through parallel norm comptutation
  \end{itemize}

@@

  \begin{itemize}
  \item Experimental framework
  \item Methods verification
  \item Numerical experiments
  \item Challenge problem
  \end{itemize}

@@
